### 2015-05-08 abstract.tex
stuff
daily update

\selectlanguage{english}
% \renewcommand{\abstractname}{\Large{The \lego Motorcyclist robot}}
\addcontentsline{toc}{chapter}{\numberline{}Abstract}
\begin{abstract}
	\begin{verse}
	\small \textit{
	by Quentin Delhaye, Arnaud Dumont, Camille Giaux, Pierre Lasbleis and  Gauthier Roig; Université Libre de Bruxelles, 2011–2012.}
	\normalsize
	\end{verse}
\end{abstract}

\clearpage

\selectlanguage{francais}
% \renewcommand{\abstractname}{\Large{Le robot motard \lego}}
\addcontentsline{toc}{chapter}{\numberline{}Résumé}
\begin{abstract}
	\begin{verse}
	\small \textit{
	par Quentin Delhaye, Arnaud Dumont, Camille Giaux, Pierre Lasbleis et Gauthier Roig ; Université Libre de Bruxelles, 2011–2012.}
	\normalsize
	\end{verse}
\end{abstract}

>>>>

\thispagestyle{plain}% This way, we can have the page numbering in the foot.
\selectlanguage{english}
% \renewcommand{\abstractname}{\Large{The \lego Motorcyclist robot}}
\addcontentsline{toc}{chapter}{\numberline{}Abstract}
\begin{abstract}
	\begin{verse}
	\small \textit{
	by Quentin Delhaye,  Master in Computer Science and Engineering, Professional Focus, Université Libre de Bruxelles, 2014--2015.}
	\normalsize
	\end{verse}
	\begin{center}
		\textbf{Implementation of high level cryptographic protocol using a SoC platform}
	\end{center}
This is an abstract.
\end{abstract}
\clearpage

\thispagestyle{plain}
\selectlanguage{francais}
% \renewcommand{\abstractname}{\Large{Le robot motard \lego}}
\addcontentsline{toc}{chapter}{\numberline{}Résumé}
\begin{abstract}
	\begin{verse}
	\small \textit{
	par Quentin Delhaye, Master en ingénieur civil en informatique, à finalité spécialisée, Université Libre de Bruxelles, 2014--2015.}
	\normalsize
	\end{verse}
\end{abstract}
